Supporting Information for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2020-02-19 writing/anderson_ehp_supp.tex
Update years and other details in text

\author[1,*]{G. Brooke Anderson} 
\author[1,2]{Joshua Ferreri}
\author[3]{Mohammad Al-Hamdan} 
\author[3]{William Crosson} 
\author[4]{Andrea Schumacher} 
\author[5]{Seth Guikema} 
\author[6]{Steven Quiring} 
\author[7]{Dirk Eddelbuettel} 
\author[1]{Meilin Yan} 
\author[8]{Roger D. Peng}

\affil[1]{Department of Environmental \& Radiological Health Sciences, Colorado 
  State University, Fort Collins, CO, 80523} 
\affil[2]{University of Colorado Anschutz Medical Campus, School of Medicine, Aurora, CO, 80045} 
\affil[3]{Universities Space Research Association, NASA Marshall Space Flight 
  Center, Huntsville, AL, 35805}
\affil[4]{Cooperative Institute for Research in the Atmosphere, Colorado State
  University, Fort Collins, CO, 80523} 
\affil[5]{Department of Industrial and Operations Engineering, University of 
  Michigan, Ann Arbor, MI, 48109}
\affil[6]{Department of Geography, Ohio State University, Columbus, OH, 43210}
\affil[7]{Department of Statistics, University of
  Illinois at Urbana-Champaign, Champaign, IL, 61820} 
\affil[8]{Department of Biostatistics, Johns Hopkins Bloomberg School of Public 
  Health, Baltimore, MD, 21205}
\affil[*]{Corresponding author: Brooke Anderson, brooke.anderson@colostate.edu}

>>>>

\author[1,*]{G. Brooke Anderson} 
\author[1,2]{Joshua Ferreri}
\author[3]{Mohammad Al-Hamdan} 
\author[3]{William Crosson} 
\author[4]{Andrea Schumacher} 
\author[5]{Seth Guikema} 
\author[6]{Steven Quiring} 
\author[7]{Dirk Eddelbuettel} 
\author[1,8]{Meilin Yan} 
\author[9]{Roger D. Peng}

\affil[1]{Department of Environmental \& Radiological Health Sciences, Colorado 
  State University, Fort Collins, CO, 80523} 
\affil[2]{University of Colorado Anschutz Medical Campus, School of Medicine, Aurora, CO, 80045} 
\affil[3]{Universities Space Research Association, NASA Marshall Space Flight 
  Center, Huntsville, AL, 35805}
\affil[4]{Cooperative Institute for Research in the Atmosphere, Colorado State
  University, Fort Collins, CO, 80523} 
\affil[5]{Department of Industrial and Operations Engineering, University of 
  Michigan, Ann Arbor, MI, 48109}
\affil[6]{Department of Geography, Ohio State University, Columbus, OH, 43210}
\affil[7]{Department of Statistics, University of
  Illinois at Urbana-Champaign, Champaign, IL, 61820} 
\affil[8]{Beijing Innovation Center for Engineering Science and Advanced Technology 
  and State Key Joint Laboratory of Environmental Simulation and Pollution Control, 
  Peking University, Beijing, China, 100871}
\affil[9]{Department of Biostatistics, Johns Hopkins Bloomberg School of Public 
  Health, Baltimore, MD, 21205}
\affil[*]{Corresponding author: Brooke Anderson, brooke.anderson@colostate.edu}

### 2020-02-19 writing/ehp_abstract.tex
Update years and other details in text

\noindent \textbf{Background:} 
        Tropical cyclone epidemiology can be 
	advanced through county-level exposure assessment methods that are comprehensive and 
	consistent across space and time, facilitating multi-year, multi-storm studies. 
	Further, an understanding of 
	patterns in and between exposure metrics that are based on specific hazards of the storm can help in 
	designing tropical cyclone epidemiological studies.\\ 
\textbf{Objectives:} (1)~Provide an open-source dataset for tropical
	cyclone exposure assessment for epidemiological research and
	(2)~investigate patterns and agreement between county-level assessments of tropical cyclone
	exposure based on different storm hazards. \\ 
\textbf{Methods:} We created an open-source dataset with county-level data on
	exposure to four tropical cyclone hazards: peak sustained wind,
	rainfall, flooding, and tornadoes. The data cover all eastern \ac{US} counties 
	for all land-falling or near-land
	Atlantic basin storms, covering~1996\,--\,2011 for all
	metrics and up to~1988\,--\,2015 for specific metrics. 	
	We validated 
	measurements against other data sources and investigated patterns
	and agreement among binary exposure classifications based on these
	metrics, as well as compared them to use of distance from the storm's track as a proxy for
	exposure.\\ 
\textbf{Results:} We describe how we developed this dataset and explore how its
	measurements compare to other data that could be used to characterize
	tropical cyclone hazards for epidemiological research. Measurements in
	the dataset created here typically agreed with data from other sources,
	and we present and discuss areas of disagreement and other caveats for
	the data. Tropical cyclones typically brought different hazards to different
	counties, and so agreement was usually low between distance-based tropical
	cyclone exposure assessment and each hazard-specific metric, as well as 
	between pairs of hazard-specific metrics. \\
\textbf{Discussion:} Our results provide a multi-hazard dataset that can be
	leveraged for epidemiologic research on tropical cyclones, as well as 
	insights that can inform the design of tropical cyclone epidemiological 
	studies.
\end{abstract}

>>>>

\noindent \textbf{Background:} 
        Tropical cyclone epidemiology can be 
	advanced through exposure assessment methods that are comprehensive and 
	consistent across space and time, as these facilite multi-year, multi-storm studies. 
	Further, an understanding of 
	patterns in and between exposure metrics that are based on specific hazards of the storm can help in 
	designing tropical cyclone epidemiologic research.\\ 
\textbf{Objectives:} (1)~Provide an open-source dataset for tropical
	cyclone exposure assessment for epidemiological research and
	(2)~investigate patterns and agreement between county-level assessments of tropical cyclone
	exposure based on different storm hazards. \\ 
\textbf{Methods:} We created an open-source dataset with county-level data on
	exposure to four tropical cyclone hazards: peak sustained wind,
	rainfall, flooding, and tornadoes. The data cover all eastern \ac{US} counties 
	for all land-falling or near-land
	Atlantic basin storms, covering~1996\,--\,2011 for all
	metrics and up to~1988\,--\,2018 for specific metrics. 	
	We validated 
	measurements against other data sources and investigated patterns
	and agreement among binary exposure classifications based on these
	metrics, as well as compared them to use of distance from the storm's track as a proxy for
	exposure.\\ 
\textbf{Results:} Our open-source dataset was typically consistent with data from other sources,
	and we present and discuss areas of disagreement and other caveats. Over the 
	study period and area, tropical cyclones typically brought different hazards to different
	counties. Therefore, when comparing exposure assessment between
	different hazard-specific metrics, agreement was usually low, as it also was when 
	comparing exposure assessment based on a distance-based proxy measurement and 
	any of the hazard-specific metrics.\\
\textbf{Discussion:} Our results provide a multi-hazard dataset that can be
	leveraged for epidemiologic research on tropical cyclones, as well as 
	insights that can inform the design and analysis for tropical cyclone epidemiologic 
	research.
\end{abstract}

### 2020-02-19 writing/ehp_cover.tex
Update years and other details in text

\author[1,*]{G.~Brooke Anderson} 
\author[1,2]{Joshua Ferreri}
\author[3]{Mohammad Al-Hamdan} 
\author[3]{William Crosson} 
\author[4]{Andrea Schumacher} 
\author[5]{Seth Guikema} 
\author[6]{Steven Quiring} 
\author[7]{Dirk Eddelbuettel} 
\author[1]{Meilin Yan} 
\author[8]{Roger D.~Peng}

\affil[1]{Department of Environmental \& Radiological Health Sciences, Colorado 
  State University, Fort Collins, CO, 80523} 
\affil[2]{University of Colorado Anschutz Medical Campus, School of Medicine, Aurora, CO, 80045} 
\affil[3]{Universities Space Research Association, NASA Marshall Space Flight 
  Center, Huntsville, AL, 35805}
\affil[4]{Cooperative Institute for Research in the Atmosphere, Colorado State
  University, Fort Collins, CO, 80523} 
\affil[5]{Department of Industrial and Operations Engineering, University of 
  Michigan, Ann Arbor, MI, 48109}
\affil[6]{Department of Geography, Ohio State University, Columbus, OH, 43210}
\affil[7]{Department of Statistics, University of
  Illinois at Urbana-Champaign, Champaign, IL, 61820} 
\affil[8]{Department of Biostatistics, Johns Hopkins Bloomberg School of Public 
  Health, Baltimore, MD, 21205}
\affil[*]{Corresponding author: G.~Brooke Anderson, brooke.anderson@colostate.edu,
  1681 Campus Delivery, Fort Collins, CO, 80523}

>>>>

\author[1,*]{G.~Brooke Anderson} 
\author[1,2]{Joshua Ferreri}
\author[3]{Mohammad Al-Hamdan} 
\author[3]{William Crosson} 
\author[4]{Andrea Schumacher} 
\author[5]{Seth Guikema} 
\author[6]{Steven Quiring} 
\author[7]{Dirk Eddelbuettel} 
\author[1,8]{Meilin Yan} 
\author[9]{Roger D.~Peng}

\affil[1]{Department of Environmental \& Radiological Health Sciences, Colorado 
  State University, Fort Collins, CO, 80523} 
\affil[2]{University of Colorado Anschutz Medical Campus, School of Medicine, Aurora, CO, 80045} 
\affil[3]{Universities Space Research Association, NASA Marshall Space Flight 
  Center, Huntsville, AL, 35805}
\affil[4]{Cooperative Institute for Research in the Atmosphere, Colorado State
  University, Fort Collins, CO, 80523} 
\affil[5]{Department of Industrial and Operations Engineering, University of 
  Michigan, Ann Arbor, MI, 48109}
\affil[6]{Department of Geography, Ohio State University, Columbus, OH, 43210}
\affil[7]{Department of Statistics, University of
  Illinois at Urbana-Champaign, Champaign, IL, 61820} 
\affil[8]{Beijing Innovation Center for Engineering Science and Advanced Technology 
  and State Key Joint Laboratory of Environmental Simulation and Pollution Control, 
  Peking University, Beijing, China, 100871}
\affil[9]{Department of Biostatistics, Johns Hopkins Bloomberg School of Public 
  Health, Baltimore, MD, 21205}
\affil[*]{Corresponding author: G.~Brooke Anderson, brooke.anderson@colostate.edu,
  1681 Campus Delivery, Fort Collins, CO, 80523}

### 2020-02-19 writing/ehp_figures.tex
Update years and other details in text

\begin{figure}[tbhp!] \centering
\includegraphics[width=\linewidth]{hurrtracks}
\caption{Study area and storms considered in this study. All counties in the states
	shown in this map were investigated. The lines show the paths of the
	study storms, which included all tracked storms in 1988\,--\,2015 that
	are recorded in \ac{HURDAT2} and that came
	within 250~\si{\kilo\metre} of at least one \ac{US} county. Thicker
	lines show the tracks of storms whose names have been retired,
	indicating that the storm was particularly severe or had notable
	impacts.  }
\label{fig:hurrtracks}
\end{figure}

@@

\begin{figure}%[tbhp] 
\centering
\includegraphics[width=7cm]{averageexposureonly.pdf} 
\caption{Average number of county-level storm exposures per decade for binary 
	classifications based on each
	single-hazard exposure metric (Table \ref{tab:exposuremetrics}). The years used to
	estimate these averages are based on years of available exposure data
	(rain: 1988\,--\,2011; wind:~1988\,--\,2015; flood and
	tornado events:~1996\,--\,2015). } 
\label{fig:averageexposure} 
\end{figure}

>>>>

\begin{figure}[tbhp!] \centering
\includegraphics[width=\linewidth]{hurrtracks}
\caption{Study area and storms considered in this study. All counties in the states
	shown in this map were investigated. The lines show the paths of the
	study storms, which included all tracked storms in 1988\,--\,2018 that
	are recorded in \ac{HURDAT2} and that came
	within 250~\si{\kilo\metre} of at least one \ac{US} county. Thicker
	lines show the tracks of storms whose names have been retired,
	indicating that the storm was particularly severe or had notable
	impacts.  }
\label{fig:hurrtracks}
\end{figure}

@@

\begin{figure}%[tbhp] 
\centering
\includegraphics[width=7cm]{averageexposureonly.pdf} 
\caption{Average number of county-level storm exposures per decade for binary 
	classifications based on each
	single-hazard exposure metric (Table \ref{tab:exposuremetrics}). The years used to
	estimate these averages are based on years of available exposure data
	(rain: 1988\,--\,2011; wind:~1988\,--\,2018; flood events:~1996\,--\,2018, and
	tornado events:~1988\,--\,2018). } 
\label{fig:averageexposure} 
\end{figure}

### 2020-02-19 writing/ehp_methods.tex
Update years and other details in text

We aggregated these data for all counties in the eastern half of the \ac{US}
(Figure~\ref{fig:hurrtracks}).  We included all tropical cyclones in
\ac{HURDAT2} \parencite{landsea2013} that came within~250 \si{\kilo\metre} of
at least one eastern \ac{US} county between 1988 and 2015.  This ensured we
were including all land-falling or near-land Atlantic basin tropical cyclones
in this period (the tracks of the study storms are shown in
Figure~\ref{fig:hurrtracks}).

@@

To identify flood- and tornado-based tropical cyclone exposures in \ac{US}
counties, we matched storm tracks with event listings from the National Oceanic
and Atmospheric Administration (NOAA)'s Storm Event
Database~\parencite{stormevents}. While this database has recorded storm data
since~1950, its coverage changed substantially in~1996 to cover more types of
storm events~\parencite{stormevents}. We therefore only considered these
metrics of hurricane exposure for tropical cyclones in~1996 and later.

@@

The tornado observations from this dataset form a traditional tornado event
database for the \ac{US}, and so we did not further validate
the tornado event data. It is difficult to characterize flooding at the county
level because flooding can be very localized and can be triggered by a variety
of causes. To investigate the extent to which the NOAA flood event listings
capture extremes that might be identified with other flooding data sources, we
investigated a sample of study counties, comparing the flood event data during
tropical storms with streamflow measurements at \ac{US} Geological Survey
county streamflow gages \parencite{usgsgages, countyfloods, dataRetrieval}.  
We considered nine study counties, selecting counties geographically spread
through storm-prone areas of the eastern \ac{US} and with multiple streamflow
gages reporting data during events. The sample counties were: Baltimore County,
MD; Bergen County, NJ; Escambia County, FL; Fairfield County, CT; Fulton
County, GA; Harris County, TX; Mobile County, AL; Montgomery County, PL; and
Wake County, NC. For each county, we first identified all streamflow gages in
the county with complete data for Jan.~1~1996\,--\,Dec.~31,~2015. If a storm
did not come within~500~\si{\kilo\metre} of a county, it was excluded from this
analysis, but all other study storms were considered. 
For each storm and county, we summed streamflow measurements across all county
gages to generate daily totals for the five-day window around the storm's
closest approach. We took the maximum of these daily streamflow totals as a
measure of the county's maximum daily streamflow during that storm. We also
calculated the percent of streamflow gages in the county with a daily
streamflow that exceeded a threshold of flooding (the streamgage's median value
for annual peak flow) on any day during the five-day
window. We investigated how these measurements varied between storms with
associated flood events listings versus storms without an
event listing for the county, to explore if storms with flood event listings
tended to be associated with higher streamflow at gages within the county.

@@

We characterized patterns in county-level exposure in the eastern \ac{US} for
exposure assessment based on each of the measured tropical cyclone hazards
(cumulative precipitation, peak sustained winds, flooding, and tornadoes).
Depending on available exposure data, this assessment included some or all of
the period from~1988 to~2015 (Table 1). For each binary metric of exposure to a
tropical cyclone hazard, we first summed the total number of county-level
exposures over available years and mapped patterns in
these exposures.

>>>>

We aggregated these data for all counties in the eastern half of the \ac{US}
(Figure~\ref{fig:hurrtracks}).  We included all tropical cyclones in
\ac{HURDAT2} \parencite{landsea2013} that came within~250 \si{\kilo\metre} of
at least one eastern \ac{US} county between 1988 and 2018.  This ensured we
were including all land-falling or near-land Atlantic basin tropical cyclones
in this period (the tracks of the study storms are shown in
Figure~\ref{fig:hurrtracks}).

@@

To identify flood- and tornado-based tropical cyclone exposures in \ac{US}
counties, we matched storm tracks with event listings from the National Oceanic
and Atmospheric Administration (NOAA)'s Storm Event
Database~\parencite{stormevents}. While this database has recorded storm data,
particularly tornadoes, since~1950, its coverage changed substantially in~1996
to cover more types of storm events, including flood
events~\parencite{stormevents}. We therefore only considered flood metrics of
hurricane exposure for tropical cyclones in~1996 and later.

@@

The tornado observations from this dataset form a traditional tornado event
database for the \ac{US}, and so we did not further validate
the tornado event data. It is difficult to characterize flooding at the county
level because flooding can be very localized and can be triggered by a variety
of causes. To investigate the extent to which the NOAA flood event listings
capture extremes that might be identified with other flooding data sources, we
investigated a sample of study counties, comparing the flood event data during
tropical storms with streamflow measurements at \ac{US} Geological Survey
county streamflow gages \parencite{usgsgages, countyfloods, dataRetrieval}.  
We considered nine study counties, selecting counties geographically spread
through storm-prone areas of the eastern \ac{US} and with multiple streamflow
gages reporting data during events. The sample counties were: Baltimore County,
MD; Bergen County, NJ; Escambia County, FL; Fairfield County, CT; Fulton
County, GA; Harris County, TX; Mobile County, AL; Montgomery County, PL; and
Wake County, NC. For each county, we first identified all streamflow gages in
the county with complete data for Jan.~1~1996\,--\,Dec.~31,~2018. If a storm
did not come within~500~\si{\kilo\metre} of a county, it was excluded from this
analysis, but all other study storms were considered. 
For each storm and county, we summed streamflow measurements across all county
gages to generate daily totals for the five-day window around the storm's
closest approach. We took the maximum of these daily streamflow totals as a
measure of the county's maximum daily streamflow during that storm. We also
calculated the percent of streamflow gages in the county with a daily
streamflow that exceeded a threshold of flooding (the streamgage's median value
for annual peak flow) on any day during the five-day
window. We investigated how these measurements varied between storms with
associated flood events listings versus storms without an
event listing for the county, to explore if storms with flood event listings
tended to be associated with higher streamflow at gages within the county.

@@

We characterized patterns in county-level exposure in the eastern \ac{US} for
exposure assessment based on each of the measured tropical cyclone hazards
(cumulative precipitation, peak sustained winds, flooding, and tornadoes).
Depending on available exposure data, this assessment included some or all of
the period from~1988 to~2018 (Table 1). For each binary metric of exposure to a
tropical cyclone hazard, we first summed the total number of county-level
exposures over available years and mapped patterns in
these exposures.

### 2020-02-19 writing/ehp_supp.tex
Update years and other details in text

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.7\linewidth]{figures/hurrtracks}
\caption{Tracks of all tropical cyclones included in the study. The study included all tracked storms in the revised Atlantic hurricane database (HURDAT2 \cite{landsea2013}) that came within 250 kilometers of at least on U.S. county, 1988--2015. Thicker lines show the tracks of storms whose names were retired, indicating that the storm was particularly severe or had notable impacts \cite{retirednames}.}
\label{fig:hurrtracks}
\end{figure}

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.6\linewidth]{figures/windcomparison}
\caption{Comparison of estimated wind categories from modeled sustained wind speed (as used for the wind exposure metric in the main text; \cite{stormwindmodel}) versus sustained wind speed determined from the revised Atlantic hurricane database (HURDAT2 \cite{landsea2013}). In HURDAT2, wind radii were available for study storms from 2004--2015 and gives estimates of the maximum radii to which storm winds of 34 knots, 50 knots, and 64 knots extended in each four quadrant of the storm at each of the six-hour storm track observations. We interpolated this data to 15-minute increments and assessed a county as exposed to winds at or above one of these cutoffs if its population mean center was within 85\% of the maximum radius for that wind speed in its quadrant of the storm. For each county in each of the available storms, we also calculated the modeled wind speed \cite{stormwindmodel} and then categorized this value into the same categories available for the HURDAT2 wind radii ($<$34 knots; 34--49.9 knots; 50--63.9 knots; $\ge$64 knots). Each point in this graph shows, for a storm, the percent of counties in which the wind category ($<$34 knots; 34--49.9 knots; 50--63.9 knots; $\ge$64 knots) was the same based on both modeled winds and the HURDAT2 wind radii. Only storms with at least one county with sustained wind of $\ge$34 knots, based on the HURDAT2 wind radii, are shown. Hurricanes Sandy (2012) and Ike (2008) were he two storms with the worst agreement between these two sets of wind data; maps with further comparisons between the two data sources for these two storms are given in Fig. \ref{fig:windexamples}.}
\label{fig:windcomparison}
\end{figure}

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.8\linewidth]{figures/floodcomparison}
\caption{Comparison of for a sample of study counties of flood status, based on NOAA Storm Events listings \cite{stormevents, noaastormevents}, with total streamflows at county streamflow gages during tropical storms \cite{usgsgages, countyfloods, dataRetrieval}. Each panel represents a separate county. For each county, we first identified all streamflow gages in the county that had complete data for Jan. 1 1996--Dec. 31, 2015. The number of streamflow gages meeting this criterion are given in parentheses beside the county's name in the panel title. This analysis covered tropical storm that came within 500 kilometers of each sample county between 1996 and 2015. In the graphs, each point represents a single tropical storm, and the point's position along the x-axis shows the highest daily total streamflow (cubic feet / second), summed across all identified streamgages in the county, for a five-day window centered on the day of the storm's closest approach to the county. The y-axis separates storms for which a flood event was reported in NOAA's Storm Events database for the county with a start date within the five-day window of the storm's closest approach to the county \cite{stormevents, noaastormevents}. Boxplots are added to show the distribution of the total streamflow measurements across storms in the county for storms grouped by whether or not they were linked with a flood event based on the NOAA Storm Events data. The color of each point gives the percent of streamflow gages in the county with a daily streamflow that exceeded a threshold of flooding (the streamgage's median value for annual peak flow \cite{countyfloods}) on any day during the five-day window.  Note that the x-axis scales differ by county, depending on the number of streamflow gages and typical flow rates for each gage, and are on a log-10 scale.}
\label{fig:floodcomparison}
\end{figure}

>>>>

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.7\linewidth]{figures/hurrtracks}
\caption{Tracks of all tropical cyclones included in the study. The study included all tracked storms in the revised Atlantic hurricane database (HURDAT2 \cite{landsea2013}) that came within 250 kilometers of at least on U.S. county, 1988--2018. Thicker lines show the tracks of storms whose names were retired, indicating that the storm was particularly severe or had notable impacts \cite{retirednames}.}
\label{fig:hurrtracks}
\end{figure}

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.6\linewidth]{figures/windcomparison}
\caption{Comparison of estimated wind categories from modeled sustained wind speed (as used for the wind exposure metric in the main text; \cite{stormwindmodel}) versus sustained wind speed determined from the revised Atlantic hurricane database (HURDAT2 \cite{landsea2013}). In HURDAT2, wind radii were available for study storms from 2004--2018 and gives estimates of the maximum radii to which storm winds of 34 knots, 50 knots, and 64 knots extended in each four quadrant of the storm at each of the six-hour storm track observations. We interpolated this data to 15-minute increments and assessed a county as exposed to winds at or above one of these cutoffs if its population mean center was within 85\% of the maximum radius for that wind speed in its quadrant of the storm. For each county in each of the available storms, we also calculated the modeled wind speed \cite{stormwindmodel} and then categorized this value into the same categories available for the HURDAT2 wind radii ($<$34 knots; 34--49.9 knots; 50--63.9 knots; $\ge$64 knots). Each point in this graph shows, for a storm, the percent of counties in which the wind category ($<$34 knots; 34--49.9 knots; 50--63.9 knots; $\ge$64 knots) was the same based on both modeled winds and the HURDAT2 wind radii. Only storms with at least one county with sustained wind of $\ge$34 knots, based on the HURDAT2 wind radii, are shown. Hurricanes Sandy (2012) and Ike (2008) were he two storms with the worst agreement between these two sets of wind data; maps with further comparisons between the two data sources for these two storms are given in Fig. \ref{fig:windexamples}.}
\label{fig:windcomparison}
\end{figure}

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.8\linewidth]{figures/floodcomparison}
\caption{Comparison of for a sample of study counties of flood status, based on NOAA Storm Events listings \cite{stormevents, noaastormevents}, with total streamflows at county streamflow gages during tropical storms \cite{usgsgages, countyfloods, dataRetrieval}. Each panel represents a separate county. For each county, we first identified all streamflow gages in the county that had complete data for Jan. 1 1996--Dec. 31, 2018. The number of streamflow gages meeting this criterion are given in parentheses beside the county's name in the panel title. This analysis covered tropical storm that came within 500 kilometers of each sample county between 1996 and 2015. In the graphs, each point represents a single tropical storm, and the point's position along the x-axis shows the highest daily total streamflow (cubic feet / second), summed across all identified streamgages in the county, for a five-day window centered on the day of the storm's closest approach to the county. The y-axis separates storms for which a flood event was reported in NOAA's Storm Events database for the county with a start date within the five-day window of the storm's closest approach to the county \cite{stormevents, noaastormevents}. Boxplots are added to show the distribution of the total streamflow measurements across storms in the county for storms grouped by whether or not they were linked with a flood event based on the NOAA Storm Events data. The color of each point gives the percent of streamflow gages in the county with a daily streamflow that exceeded a threshold of flooding (the streamgage's median value for annual peak flow \cite{countyfloods}) on any day during the five-day window.  Note that the x-axis scales differ by county, depending on the number of streamflow gages and typical flow rates for each gage, and are on a log-10 scale.}
\label{fig:floodcomparison}
\end{figure}
